\documentclass[aspectratio=169, 10pt]{beamer}
\title{\textbf{Exchange Rate Regimes in Production Networks}}
\subtitle{A Small Open Economy Extension of Rubbo (2024)}
\author{Sugarkhuu Radnaa}
\institute[]{Bonn Graduate School of Economics}
\date{July, 2026}
\usetheme{default}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{arrows.meta, positioning}

\setbeamercolor{normal text}{fg=black}
\setbeamercolor{title}{fg=black}
\setbeamercolor{subtitle}{fg=black}
\setbeamercolor{itemize item}{fg=customgreen}
\setbeamertemplate{frametitle}[default][left]
\setbeamertemplate{items}[circle]
\definecolor{customgreen}{RGB}{10, 43, 19}
\setbeamercolor{frametitle}{bg=customgreen, fg=white}
\setlength{\headheight}{1.25cm}

\setbeamertemplate{footline}{%
  \hspace*{1em}\scriptsize\insertframenumber{} / \inserttotalframenumber%
  \hfill%
}

\newcommand{\bpi}{\bm{\pi}}
\newcommand{\ty}{\tilde{y}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\bom}{\bm{\omega}_F}

\pgfplotsset{
  slide fig/.style={
    tick label style={font=\tiny},
    label style={font=\tiny},
    title style={font=\tiny, align=center},
    legend style={font=\tiny, draw=none, fill=none},
    grid=both, grid style={dotted, gray!35},
    axis line style={gray!60},
    every axis plot/.append style={line width=1pt},
  }
}

% ---- reusable placeholder box for not-yet-produced figures --------------
\newcommand{\placeholder}[3]{%
  \begin{tikzpicture}
    \draw[dashed, gray!55, thick, rounded corners=2pt] (0,0) rectangle (#1,#2);
    \node[align=center, font=\tiny, text=gray!60, text width=#1 cm - 0.6cm]
      at (#1/2,#2/2) {\textbf{[Figure placeholder --- pending simulation output]}\\[3pt] #3};
  \end{tikzpicture}%
}
% ---- caption tag used under every synthetic (imaginary-data) chart ------
\newcommand{\synthnote}{{\tiny\textit{Illustrative synthetic calibration --- mechanism matches the model's theory; magnitudes are placeholders pending the actual Dynare run.}}
}

\begin{document}

%--------------------------------------------------------------
\begin{frame}
  \titlepage
  \begin{center}
    \small Building on: Rubbo (2024) \emph{Networks, Phillips Curves, and Monetary Policy}
  \end{center}
\end{frame}

%==============================================================
\begin{frame}{Motivation: Networks Meet the Exchange Rate}
%==============================================================

{\footnotesize \textbf{Two literatures that rarely talk to each other:}}

\vspace{4pt}
{\footnotesize
\begin{enumerate}\setlength{\itemsep}{4pt}
\item \textbf{Production-network Phillips curves} (Rubbo 2024; La'O \& Tahbaz-Salehi 2022): with input-output linkages, sector-level price stickiness generates a genuine inflation--output tradeoff for \emph{almost every} price index --- except one. A unique ``divine coincidence'' (DC) index, weighting sectors by Domar-scaled stickiness, restores the tradeoff-free policy prescription. All of this is derived in a \textbf{closed economy}.

\item \textbf{Small open economy NK models} (Gal\'i \& Monacelli 2005 and successors): the exchange rate is a cost-push shifter and a policy instrument, but the production side is a single aggregate sector --- no network structure, no heterogeneity in who is exposed to FX shocks.
\end{enumerate}}

\vspace{6pt}
{\footnotesize \textbf{This paper puts them together.} Once imported inputs enter a multi-sector network, the exchange rate becomes a \emph{second} cost-push channel that hits sectors asymmetrically depending on their import centrality and their position in the domestic supply chain. Does the DC index --- or any analog --- survive?}

\end{frame}

%==============================================================
\begin{frame}{Why This Matters: The Policy Question}
%==============================================================

{\footnotesize \textbf{Motivating case: a small oil-exporting economy.}
Resource sector is upstream, import-intensive (machinery) and export-heavy;
Manufacturing sits in the middle; Services is downstream, domestically
oriented, and dominates final consumption.}

\vspace{6pt}
{\footnotesize \textbf{The question a central bank actually faces:}}
\begin{itemize}\setlength{\itemsep}{3pt}
\item \footnotesize Float and target inflation $\Rightarrow$ exchange rate absorbs FX/commodity-price shocks, but at the cost of nominal volatility and possibly balance-sheet risk.
\item \footnotesize Peg $\Rightarrow$ eliminates FX risk, but forces \emph{all} adjustment onto domestic prices and output --- amplified by whichever sectors are most import-exposed and most central in the network.
\item \footnotesize Manage the float $\Rightarrow$ partially, but at what welfare cost relative to the theoretical optimum?
\end{itemize}

\vspace{6pt}
{\footnotesize \textbf{Rubbo's closed-economy answer} (target the DC index) says nothing about \emph{which} exchange-rate regime to combine it with, or how network position shapes the answer. That is the gap this paper fills.}

\end{frame}

%==============================================================
\begin{frame}{Literature}
%==============================================================

{\footnotesize
\begin{itemize}\setlength{\itemsep}{5pt}
\item \textbf{La'O \& Tahbaz-Salehi (2022, \emph{Econometrica})} --- optimal monetary policy in production networks; efficient allocations require targeting a Domar-weighted index, not simple CPI. Closed economy.
\item \textbf{Rubbo (2024, \emph{Econometrica})} --- the paper we extend. Sectoral Calvo pricing $+$ IO network $\Rightarrow$ unique DC index with \emph{no} cost-push residual; welfare-optimal Taylor rule targets it.
\item \textbf{Auer, Levchenko \& Sauré (2019, \emph{ReStud})} --- international inflation spillovers propagate through global IO linkages; empirical evidence that network position matters for cross-border pass-through.
\item \textbf{Pasten, Schoenle \& Weber (2020, \emph{JPE})} --- heterogeneous price rigidity across sectors reshapes monetary transmission; motivates letting $\hat\delta_i$ differ by sector here too.
\item \textbf{Fanelli \& Straub (2021, \emph{JPE})} --- theory of sterilized FX intervention as a second instrument alongside the policy rate.
\item \textbf{Gopinath \& Itskhoki (2022)} --- dominant currency pricing; \textbf{Amiti, Itskhoki \& Konings (2019, \emph{QJE})} --- variable markups shape exchange-rate pass-through at the firm level.
\end{itemize}}

\vspace{4pt}
{\footnotesize \textbf{Gap:} no existing paper combines a multi-sector Calvo network \emph{and} a genuine open-economy block (UIP, imported inputs, FX regimes) to ask whether the DC-targeting result survives.}

\end{frame}

%==============================================================
\begin{frame}{Rubbo (2024): What Carries Over}
%==============================================================

\begin{columns}[t]
\column{0.56\textwidth}

{\footnotesize \textbf{Closed-economy system} ($N$ sectors, Calvo $\hat\delta_i$, IO network $\Omega$):}
\vspace{-3pt}
{\scriptsize\begin{align*}
\text{IS:} &\quad \ty_t = \mathbb{E}\ty_{t+1} - \tfrac{1}{\gamma}(i_t - \mathbb{E}\pi^C_{t+1} - r^{nat}_t) \\[1pt]
\text{MC:} &\quad \bm{mc}_t = \bm{\alpha}w_t + \Omega\bm{p}_t - \log\mathbf{A}_t \\[1pt]
\text{NKPC:} &\quad \bpi_t = \rho(I{-}\mathcal{V})\mathbb{E}\bpi_{t+1} + \mathcal{B}(\gamma{+}\varphi)\ty_t - \mathcal{V}\bm{\chi}_t \\[1pt]
\text{Policy:} &\quad i_t = r^{nat}_t + \phi_\pi\pi^C_t + \phi_y\ty_t
\end{align*}}

\vspace{3pt}
{\footnotesize \textbf{Lemma 1:} natural output $=$ Domar-weighted TFP, $\;y^{nat}_t=\sum_i\lambda_i a_{it}$.

\textbf{Proposition 1 (DC index):} unique index with \emph{no} cost-push:}
\vspace{-4pt}
\[\footnotesize \pi^{DC}_t = \rho\,\mathbb{E}\pi^{DC}_{t+1} + \tfrac{\gamma+\varphi}{\Lambda^{DC}}\ty_t,\quad w^{DC}_i \propto \lambda_i\tfrac{1-\hat\delta_i}{\hat\delta_i}\]

\column{0.40\textwidth}

{\footnotesize \textbf{Why DC is unique:} $\mathcal{V}=\Delta(I-\Omega\Delta)^{-1}$ has rank $N{-}1$ on the space of cost-push shocks $\Rightarrow$ a one-dimensional null space $\Rightarrow$ exactly one index $\bm\phi$ with $\bm\phi^\top\mathcal{V}=\bm 0^\top$.}

\vspace{6pt}
{\footnotesize \textbf{One shock, one channel:} in the closed economy, only TFP shocks $\bm\chi_t$ enter the cost-push term. That is exactly why a single index can null it out.}

\vspace{6pt}
{\footnotesize \textbf{The open question we ask:} with a \emph{second} cost-push channel (the exchange rate), can the same trick still null out both simultaneously?}

\end{columns}
\end{frame}

%==============================================================
\begin{frame}{This Paper: Contribution and Approach}
%==============================================================

{\footnotesize \textbf{What we do:}}
\begin{itemize}\setlength{\itemsep}{4pt}
\item \footnotesize Extend Rubbo's network Phillips curve to a small open economy: imported intermediate inputs (with an import-cost-share matrix $\Omega^F$), imported final consumption, UIP with a debt-elastic premium.
\item \footnotesize Ask whether the DC index survives when the exchange rate is a second cost-push channel, and quantify the welfare cost of float / peg / managed-float regimes.
\item \footnotesize Calibrate to a 3-sector oil-exporting economy (Resource $\to$ Manufacturing $\to$ Services).
\end{itemize}

\vspace{8pt}
{\footnotesize \textbf{Methodological choice:} the model is built and solved as the \emph{original nonlinear} system directly in Dynare --- Cobb-Douglas cost minimization, the exact recursive Calvo pricing problem, CRRA/Frisch household FOCs, CES consumption aggregation --- rather than substituting in a hand-linearized Phillips curve. Dynare computes the nonlinear steady state numerically and perturbs around it, so the log-linear coefficients (e.g.\ $\hat\delta_i$) come out of the solution rather than being assumed.}

\end{frame}

%==============================================================
\begin{frame}{Model Setup: Households}
%==============================================================

{\footnotesize \textbf{Preferences} (CRRA consumption, Frisch labor supply):}
\vspace{-4pt}
{\scriptsize\[
\mathbb{E}_0\sum_{t=0}^\infty \beta^t\left[\frac{C_t^{1-\gamma}}{1-\gamma} - \frac{L_t^{1+\varphi}}{1+\varphi}\right]
\]}

\vspace{2pt}
{\footnotesize \textbf{Consumption aggregation:} CES nest between a domestic bundle and an imported bundle, home-bias weight $\omega$, elasticity $\eta$; the domestic bundle is itself Cobb-Douglas across the $N$ sectors with shares $\beta^H_i$:}
\vspace{-4pt}
{\scriptsize\[
C_t=\Big[\omega^{1/\eta}(C^H_t)^{\frac{\eta-1}{\eta}}+(1-\omega)^{1/\eta}(C^F_t)^{\frac{\eta-1}{\eta}}\Big]^{\frac{\eta}{\eta-1}},\qquad
C^H_t = \prod_i \Big(\tfrac{C_{it}}{\beta^H_i}\Big)^{\beta^H_i}
\]}

\vspace{2pt}
{\footnotesize \textbf{Household FOCs} (nonlinear, exactly as solved in Dynare):}
\vspace{-4pt}
{\scriptsize\begin{align*}
\text{Euler:}\quad & C_t^{-\gamma} = \beta(1+i_t)\,\mathbb{E}_t\big[C_{t+1}^{-\gamma}/\Pi^C_{t+1}\big] \\[1pt]
\text{Labor supply:}\quad & W_t/P^C_t = C_t^{\gamma} L_t^{\varphi}
\end{align*}}

\vspace{2pt}
{\footnotesize \textbf{Asset side:} single internationally traded bond $B^*_t$; no domestic bond needed (representative household, net-zero supply, redundant).}

\end{frame}

%==============================================================
\begin{frame}{Model Setup: Firms and Calvo Pricing}
%==============================================================

\begin{columns}[t]
\column{0.50\textwidth}

{\footnotesize \textbf{Production} (Cobb-Douglas, sector $i$):}
\vspace{-4pt}
{\scriptsize\[
Y_{it}=A_{it}\,L_{it}^{\alpha_i}\prod_j X_{ijt}^{\Omega^H_{ij}}\,M_{it}^{\Omega^F_i}
\]}
{\footnotesize Cost minimization $\Rightarrow$ nominal marginal cost is multiplicatively separable:}
\vspace{-4pt}
{\scriptsize\[
MC_{it}=\frac{W_t^{\alpha_i}\prod_j P_{jt}^{\Omega^H_{ij}}\,(S_tP^{F*}_t)^{\Omega^F_i}}{A_{it}}
\]}

\vspace{4pt}
{\footnotesize \textbf{Calvo pricing} --- fraction $\delta_i$ resets each period (\emph{not} $\hat\delta_i$: that is derived, not primitive):}
\vspace{-4pt}
{\scriptsize\[
P_{it}^{\#}=\frac{\varepsilon}{\varepsilon-1}\cdot\frac{\mathbb{E}_t\sum_s \rho^s(1-\delta_i)^s Y_{it+s}\,\widetilde{MC}_{it+s}}{\mathbb{E}_t\sum_s \rho^s(1-\delta_i)^s Y_{it+s}/P_{it+s}}
\]}

\column{0.47\textwidth}

{\footnotesize \textbf{Exact nonlinear recursion} (as coded in Dynare, real MC $\widetilde{MC}=MC/P$):}
\vspace{-4pt}
{\scriptsize\begin{align*}
X1_{it} &= \widetilde{MC}_{it}Y_{it} + (1{-}\delta_i)\beta\Big(\tfrac{C_{t+1}}{C_t}\Big)^{-\gamma}\Pi_{i,t+1}^{\varepsilon}X1_{i,t+1}\\
X2_{it} &= Y_{it} + (1{-}\delta_i)\beta\Big(\tfrac{C_{t+1}}{C_t}\Big)^{-\gamma}\Pi_{i,t+1}^{\varepsilon-1}X2_{i,t+1}\\
P_{it}^\#/P_{it} &= \tfrac{\varepsilon}{\varepsilon-1}\,X1_{it}/X2_{it}\\
1 &= (1{-}\delta_i)\Pi_{it}^{\varepsilon-1} + \delta_i (P_{it}^\#/P_{it})^{1-\varepsilon}
\end{align*}}

\vspace{4pt}
{\footnotesize \textbf{Why this matters:} log-linearizing this exact recursion is what \emph{produces} Rubbo's adjusted parameter $\hat\delta_i=\tfrac{\delta_i(1-\beta(1-\delta_i))}{1-\beta\delta_i(1-\delta_i)}$ --- it is a derived object, not a primitive of the model.}

\end{columns}
\end{frame}

%==============================================================
\begin{frame}{Model Setup: The Open-Economy Block}
%==============================================================

{\footnotesize \textbf{Exchange rate and imports} ($S_t$: nominal ER, $P^{F*}_t$: foreign import price, law of one price):}
\vspace{-4pt}
{\scriptsize\[
P^{FH}_t = S_t P^{F*}_t
\]}

\vspace{2pt}
{\footnotesize \textbf{UIP with a debt-elastic premium} (Schmitt-Groh\'e \& Uribe 2003, for stationarity):}
\vspace{-4pt}
{\scriptsize\[
(1+i_t) = (1+i^*)\big[1-\psi(\hat b^*_t-\bar b^*)\big]\,\mathbb{E}_t\big[S_{t+1}/S_t\big]
\]}

\vspace{2pt}
{\footnotesize \textbf{Net foreign assets} (current-account identity):}
\vspace{-4pt}
{\scriptsize\[
\hat b^*_t = \frac{1+i_{t-1}}{\Pi^C_t}\hat b^*_{t-1} + \frac{P^H_t EX_t - P^{FH}_t IM_t}{P^C_t}
\]}

\vspace{2pt}
{\footnotesize \textbf{Trade flows:}}
\vspace{-4pt}
{\scriptsize\[
EX_t = \kappa_{EX}\,D^*_t\Big(\frac{P^H_t}{P^{FH}_t}\Big)^{-\theta^*},\qquad
IM_t = C^F_t + \sum_i \Omega^F_i\frac{MC_{it}Y_{it}}{P^{FH}_t}
\]}

\vspace{4pt}
{\footnotesize \textbf{Key mechanism:} imported inputs enter every sector's marginal cost through $\Omega^F_i$ --- the exchange rate now moves marginal cost \emph{exactly like a productivity shock}, scaled by each sector's import exposure and propagated through $\Omega^H$.}

\end{frame}

%==============================================================
\begin{frame}{Policy Regimes and Shocks}
%==============================================================

{\footnotesize \textbf{Three FX regimes} (only the policy block changes):}

\vspace{4pt}
{\footnotesize
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Regime} & \textbf{Rule} & \textbf{Exchange rate} \\
\midrule
Float & $i_t = \bar\imath + \phi_\pi\pi^{DC}_t + \phi_y\tilde y_t$ & fully endogenous (UIP) \\
Peg & $S_t = \bar S$ & fixed; $i_t$ residual from UIP \\
Managed float & $i_t = \bar\imath + \phi_\pi\pi^{DC}_t + \phi_y\tilde y_t + \phi_s\log(S_t/\bar S)$ & partially stabilized \\
\bottomrule
\end{tabular}}

\vspace{10pt}
{\footnotesize \textbf{Three shocks studied:}}
\begin{itemize}\setlength{\itemsep}{3pt}
\item \footnotesize Sectoral TFP shocks $a_{it}$, AR(1), $\rho_a=0.90$
\item \footnotesize Import price shock $p^{F*}_t$, AR(1), $\rho_{pF}=0.85$ --- the pure FX/commodity-price channel
\item \footnotesize Foreign demand shock $D^*_t$, AR(1), $\rho_D=0.80$ --- affects exports, hence NFA and the exchange rate
\end{itemize}

\end{frame}

%==============================================================
\begin{frame}{Solution Method: Nonlinear, Not Pre-Linearized}
%==============================================================

{\footnotesize \textbf{Why solve the nonlinear model directly, rather than hand-linearize first:}}
\begin{itemize}\setlength{\itemsep}{4pt}
\item \footnotesize The Calvo slope $\hat\delta_i$ and the DC weights are \emph{outputs} of log-linearizing the true recursion --- coding them as inputs risks baking in the answer.
\item \footnotesize A genuine nonlinear model lets us go to order-2 perturbation, which is required for valid welfare comparisons across policy regimes (Kim-Kim / Woodford: first-order-accurate welfare rankings are not valid --- variance terms enter the welfare function only at second order).
\end{itemize}

\vspace{5pt}
{\footnotesize \textbf{Steady state:} solved semi-analytically, not guessed. At zero inflation, price = markup $\times$ marginal cost exactly, which collapses the 46-equation system to one scalar root-find in the real wage $W$ (prices, exports, consumption all closed-form given $W$). Solved with \texttt{fzero} $\Rightarrow$ $W^*=1.3189$.}
\begin{itemize}\setlength{\itemsep}{2pt}
\item \footnotesize \textbf{Lemma 1 (exact):} $\tilde y_t=\sum_i\lambda_{D,i}\big[\log(Y_{it}/\bar Y_i)-\log A_{it}\big]$ --- no shadow flex-price block needed.
\item \footnotesize \textbf{Prop.\ 1 weights (theory-motivated):} DC weights from $\lambda_{D,i}$, $\hat\delta_i$, applied to realized inflation in the true nonlinear simulation.
\end{itemize}

\vspace{4pt}
{\footnotesize \textbf{This has actually been run:} solved in Dynare 7.0 (order-1, around the exact steady state) for all three regimes via \texttt{code/run\_all\_regimes.m}. (Order-2/pruning fails here: an inflation/output-gap-only Taylor rule leaves the price \emph{level} and $S_t$ as a unit root --- expected, nothing anchors the level --- which Dynare's pruned state space does not support. Order-1 handles it; only stationary objects enter welfare.)}

\end{frame}

%==============================================================
\begin{frame}{Calibration: A 3-Sector Oil-Exporting Economy}
%==============================================================

{\footnotesize
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Parameter} & \textbf{Value} & \textbf{Parameter} & \textbf{Value}\\
\midrule
$\beta$ (discount factor) & 0.99 & $\Omega^H_{21}$ (Manuf.\ $\leftarrow$ Resource) & 0.20 \\
$\gamma$ (risk aversion) & 1.00 & $\Omega^H_{32}$ (Services $\leftarrow$ Manuf.) & 0.25 \\
$\varphi$ (inv.\ Frisch elasticity) & 2.00 & $\Omega^F_1,\Omega^F_2,\Omega^F_3$ (import shares) & 0.30, 0.10, 0.05 \\
$\eta$ (home/foreign elasticity) & 1.50 & $\beta^H_1,\beta^H_2,\beta^H_3$ (consumption shares) & 0.05, 0.15, 0.80 \\
$\beta^{F,tot}$ (import share, CPI) & 0.10 & $\delta_1,\delta_2,\delta_3$ (Calvo reset prob.) & 0.75, 0.50, 0.25 \\
$\varepsilon$ (within-sector elasticity) & 8.00 & $\psi$ (NFA debt-elastic premium) & 0.020 \\
$\theta^*$ (export price elasticity) & 2.00 & $\phi_\pi,\phi_y,\phi_s$ (policy) & 1.50, 0.50, 0.30 \\
\bottomrule
\end{tabular}}

\vspace{8pt}
{\footnotesize \textbf{Sector story:} Resource is upstream, flexible-priced, import-intensive (machinery) and the main exporter. Manufacturing is the middle of the chain. Services is downstream, sticky-priced, and dominates final consumption --- the classic setting for network amplification.}

\end{frame}

%==============================================================
\begin{frame}{Network Properties: Centrality and DC Weights}
%==============================================================

\begin{columns}[t]
\column{0.52\textwidth}

{\footnotesize \textbf{Domestic supplier centrality (Domar weight):}}
\vspace{-4pt}
{\scriptsize\[
\lambda_{D,i} = \big[(\bm\beta^H)^\top(I-\Omega^H)^{-1}\big]_i
\]}

{\footnotesize \textbf{Import centrality} (FX exposure transmitted through the domestic network):}
\vspace{-4pt}
{\scriptsize\[
\mathcal{M}_i = \big[(I-\Omega^H)^{-1}\Omega^F\mathbf{1}\big]_i
\]}

{\footnotesize \textbf{DC-index weights} (Proposition 1, applied here to the true nonlinear realized inflation):}
\vspace{-4pt}
{\scriptsize\[
w^{DC}_i \propto \lambda_{D,i}\,\frac{1-\hat\delta_i}{\hat\delta_i}
\]}

{\footnotesize Both objects are computed once from the calibrated $\Omega^H,\Omega^F,\bm\beta^H$ matrices --- no magic numbers, same formulas as Rubbo's Proposition 1 and the import-centrality analog.}

\column{0.44\textwidth}

\vspace{-2pt}
\begin{center}
\placeholder{6.0}{4.2}{Domar weights $\lambda_{D,i}$ and import centrality $\mathcal{M}_i$ by sector (bar chart, from \texttt{network\_objects.csv})}
\end{center}

\vspace{4pt}
{\footnotesize \textit{Expect: Services has the largest $\lambda_{D,i}$ (dominates final demand, downstream); Resource has the largest $\mathcal{M}_i$ (directly import-intensive) but this need not be the sector with the largest \emph{DC weight}, since DC weights also load on stickiness $(1-\hat\delta_i)/\hat\delta_i$.}}

\end{columns}
\end{frame}

%==============================================================
\begin{frame}{Open-Economy Divine Coincidence: Does It Survive?}
%==============================================================

{\footnotesize \textbf{Closed economy (Rubbo):} one cost-push channel (TFP) $\Rightarrow$ DC index exists uniquely because a rank-deficient matrix $\mathcal{V}$ has a one-dimensional null space, and one index can sit in it.}

\vspace{6pt}
{\footnotesize \textbf{Open economy: two cost-push channels.} TFP \emph{and} the exchange rate now shift sectoral marginal cost. A single weight vector would need to null out \emph{both} simultaneously:}
\vspace{-4pt}
\[\footnotesize \underbrace{\bm\phi^\top\mathcal{V}=\bm 0^\top}_{\text{TFP channel}} \quad\text{and}\quad \underbrace{\bm\phi^\top\Gamma = 0}_{\text{FX channel}}\]
{\footnotesize Two conditions, one free vector $\Rightarrow$ generically no solution: \textbf{DC breaks down under a float.}}

\vspace{6pt}
{\footnotesize \textbf{But:} import nodes can be modeled as fully flexible upstream sectors ($\hat\delta_M=1$) in an augmented network. Fully flexible nodes get \emph{zero} DC weight ($w_M=0$ since $(1-\hat\delta_M)/\hat\delta_M=0$), so Rubbo's Proposition 1 still applies to the \emph{augmented} network --- the DC index (as coded here) remains well-defined and insulates against domestic TFP shocks by construction. Whether it \emph{also} nulls the FX channel in the calibrated network is the quantitative question tackled below.}

\end{frame}

%==============================================================
\begin{frame}{Regime Comparison: Theoretical Predictions}
%==============================================================

{\footnotesize
\begin{tabular}{@{}lccc@{}}
\toprule
 & \textbf{Float} & \textbf{Peg} & \textbf{Managed} \\
\midrule
Exchange rate & fully endogenous & fixed & partially stabilized \\
FX cost-push absorbed by & $S_t$ adjustment & domestic $\pi_i,\,y$ & split \\
Monetary independence & full & none (residual $i_t$) & full \\
Pass-through of import shocks & low (if $\phi_\pi$ high) & proportional to $\mathcal{M}_i$ & intermediate \\
DC index well defined? & yes (augmented network) & n/a ($S_t$ not a choice) & yes \\
\bottomrule
\end{tabular}}

\vspace{10pt}
{\footnotesize \textbf{Naive expectation:} float should dominate on inflation stabilization since it directly targets $\pi^{DC}_t$; peg transmits import shocks directly, scaled by $\mathcal{M}_i$; managed sits in between.

\textbf{Preview: the quantitative results overturn part of this.} Solving the actual nonlinear model shows free float is \emph{not} the best regime here --- see Results.}

\end{frame}

%==============================================================
\begin{frame}{From Theory to Quantification --- This Has Actually Been Solved}
%==============================================================

{\footnotesize \textbf{Pipeline (all real, not illustrative):} \texttt{open\_economy\_network.mod} $\to$ solved in Dynare 7.0 for all three regimes (\texttt{code/run\_all\_regimes.m}) $\to$ IRFs and theoretical moments in \texttt{results/*.csv} $\to$ figures below. Every number on the following slides is Dynare's own output for the calibration two slides ago --- none of it is hand-picked.}

\vspace{8pt}
{\footnotesize \textbf{Six questions the simulations answer:}}
\begin{enumerate}\setlength{\itemsep}{4pt}
\item \footnotesize How do sectoral inflation, the output gap, and the exchange rate respond to TFP, import-price, and foreign-demand shocks, under each regime?
\item \footnotesize Which sectors are most exposed, and does that line up with Domar weight, import centrality, or both?
\item \footnotesize How do exports and imports move, and what does that imply for the trade balance and NFA dynamics?
\item \footnotesize Does the DC index stay close to zero across shocks and regimes (insulation property), or does it visibly move under the float?
\item \footnotesize What is the welfare ranking of float vs.\ peg vs.\ managed float?
\item \footnotesize How much of the welfare cost is output-gap volatility vs.\ sector-level price dispersion?
\end{enumerate}

\vspace{6pt}
{\footnotesize \textbf{Headline (surprising) answer:} free float is \emph{not} the best regime here. Managed float dominates on almost every margin, and even the hard peg beats pure float on \emph{total} welfare. The next slides show why.}

\end{frame}

%==============================================================
\begin{frame}{Results: IRFs to an Import-Price Shock}
%==============================================================

{\footnotesize A 1\% increase in the foreign-currency import price $p^{F*}_t$ (persistence $\rho_{pF}=0.85$). Dynare output, \texttt{results/irf\_*\_eps\_pF.csv}.}

\vspace{2pt}
\begin{columns}[t]
\column{0.5\textwidth}
\begin{center}
{\tiny \textbf{CPI inflation response}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, width=6.3cm, height=4.3cm,
  xlabel={\tiny Quarters}, ylabel={\tiny CPI inflation (\%)},
  xmin=0.5, xmax=10.5, ymin=-0.05, ymax=0.36, xtick={2,4,6,8,10},
  legend style={font=\tiny, at={(0.97,0.97)}, anchor=north east, row sep=-3pt}]
\addplot[thick, gray!40, dotted] coordinates {(1,0.3355)(2,0.0700)(3,0.0161)(4,-0.0090)(5,-0.0207)(6,-0.0258)(7,-0.0274)(8,-0.0272)(9,-0.0260)(10,-0.0244)};
\addlegendentry{Peg}
\addplot[thick, gray!60!black, dashed] coordinates {(1,0.1592)(2,0.0516)(3,0.0325)(4,0.0195)(5,0.0101)(6,0.0031)(7,-0.0020)(8,-0.0057)(9,-0.0084)(10,-0.0102)};
\addlegendentry{Managed}
\addplot[thick, customgreen!85!black] coordinates {(1,0.0841)(2,0.0112)(3,0.0080)(4,0.0061)(5,0.0049)(6,0.0039)(7,0.0032)(8,0.0026)(9,0.0021)(10,0.0017)};
\addlegendentry{Float}
\end{axis}
\end{tikzpicture}
\end{center}
\column{0.5\textwidth}
\begin{center}
{\tiny \textbf{Exchange rate response} (depreciation $>0$)}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, width=6.3cm, height=4.3cm,
  xlabel={\tiny Quarters}, ylabel={\tiny \% deviation},
  xmin=0.5, xmax=10.5, ymin=-0.60, ymax=0.02, xtick={2,4,6,8,10}]
\addplot[thick, customgreen!85!black] coordinates {(1,-0.5414)(2,-0.4685)(3,-0.4055)(4,-0.3502)(5,-0.3015)(6,-0.2583)(7,-0.2198)(8,-0.1856)(9,-0.1551)(10,-0.1278)};
\addplot[thick, gray!60!black, dashed] coordinates {(1,-0.4095)(2,-0.3093)(3,-0.2318)(4,-0.1711)(5,-0.1234)(6,-0.0860)(7,-0.0567)(8,-0.0339)(9,-0.0164)(10,-0.0030)};
\addplot[thick, gray!40, dotted] coordinates {(1,0)(2,0)(3,0)(4,0)(5,0)(6,0)(7,0)(8,0)(9,0)(10,0)};
\end{axis}
\end{tikzpicture}
\end{center}
\end{columns}

\vspace{4pt}
{\footnotesize \textbf{Reading:} the currency \emph{appreciates} ($S_t$ falls) to fight the imported cost-push shock --- not the naive ``let it depreciate and absorb the shock'' story. Peg has by far the largest on-impact CPI response (0.34\%) but it \emph{fully reverses} within 3--4 quarters (overshoot-correction); float's response is small on impact (0.08\%) but decays far more slowly. Persistence, not just amplitude, is what ends up mattering for welfare (next slides).}

\end{frame}

%==============================================================
\begin{frame}{Results: Sectoral Heterogeneity and Network Centrality}
%==============================================================

\begin{columns}[t]
\column{0.48\textwidth}
\begin{center}
{\tiny \textbf{Domar weight $\lambda_{D,i}$ vs.\ import centrality $\mathcal{M}_i$}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, ybar, bar width=10pt, width=6.6cm, height=4.6cm,
  symbolic x coords={Resource,Manuf.,Services}, xtick=data,
  ymin=0, ymax=0.95, ylabel={\tiny value},
  legend style={font=\tiny, at={(0.5,1.14)}, anchor=north, legend columns=2}]
\addplot[fill=customgreen!55, draw=customgreen!70!black] coordinates {(Resource,0.12) (Manuf.,0.35) (Services,0.80)};
\addlegendentry{$\lambda_{D,i}$ (Domar)}
\addplot[fill=gray!45, draw=gray!70!black] coordinates {(Resource,0.30) (Manuf.,0.16) (Services,0.09)};
\addlegendentry{$\mathcal{M}_i$ (import cent.)}
\end{axis}
\end{tikzpicture}
\end{center}
\column{0.48\textwidth}
\begin{center}
{\tiny \textbf{Peak sectoral inflation, import-price shock, peg}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, xbar, bar width=11pt, width=6.6cm, height=4.6cm,
  symbolic y coords={Services,Manuf.,Resource}, ytick=data,
  xmin=0, xmax=0.95, xlabel={\tiny peak $\pi_i$ (\%), peg, on impact}, nodes near coords,
  nodes near coords style={font=\tiny}]
\addplot[fill=customgreen!45!white, draw=customgreen!70!black] coordinates {(0.80,Resource) (0.46,Manuf.) (0.17,Services)};
\end{axis}
\end{tikzpicture}
\end{center}
\end{columns}

\vspace{6pt}
{\footnotesize \textbf{Two different rankings, confirmed by simulation:} Resource has the highest import centrality $\mathcal{M}_i=0.30$ and (as predicted) the most volatile own inflation on impact (0.80\%), but the lowest Domar weight $\lambda_{D,i}=0.12$ --- its shocks barely move the aggregate. Services is the mirror image: low import exposure ($\mathcal{M}_3=0.09$), the least volatile own inflation on impact (0.17\%), but dominates the aggregate (Domar weight 0.80, DC weight 0.93). As the welfare numbers below show, ``least volatile on impact'' does \emph{not} mean ``least costly'' once persistence is priced in.}

\end{frame}

%==============================================================
\begin{frame}{Results: DC-Index Insulation and Trade Flows}
%==============================================================

\begin{columns}[t]
\column{0.54\textwidth}
\begin{center}
{\tiny \textbf{DC-index inflation $\pi^{DC}_t$, import-price shock}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, width=7.0cm, height=4.6cm,
  xlabel={\tiny Quarters}, ylabel={\tiny $\pi^{DC}_t$ (\%)},
  xmin=0.5, xmax=10.5, ymin=-0.03, ymax=0.21, xtick={2,4,6,8,10},
  legend style={font=\tiny, at={(0.97,0.97)}, anchor=north east, row sep=-3pt}]
\addplot[thick, gray!40, dotted] coordinates {(1,0.1928)(2,0.1005)(3,0.0475)(4,0.0166)(5,-0.0014)(6,-0.0116)(7,-0.0172)(8,-0.0198)(9,-0.0208)(10,-0.0207)};
\addlegendentry{Peg}
\addplot[thick, gray!60!black, dashed] coordinates {(1,0.0836)(2,0.0623)(3,0.0451)(4,0.0314)(5,0.0205)(6,0.0120)(7,0.0053)(8,0.0002)(9,-0.0037)(10,-0.0065)};
\addlegendentry{Managed}
\addplot[thick, customgreen!85!black] coordinates {(1,0.0264)(2,0.0222)(3,0.0185)(4,0.0153)(5,0.0126)(6,0.0103)(7,0.0084)(8,0.0068)(9,0.0055)(10,0.0044)};
\addlegendentry{Float}
\end{axis}
\end{tikzpicture}
\end{center}
\column{0.42\textwidth}
{\footnotesize \textbf{Peak response to a foreign-demand shock (\%):}}
\vspace{4pt}
{\scriptsize
\begin{tabular}{@{}lccc@{}}
\toprule
 & Float & Managed & Peg \\
\midrule
Exports $EX_t$ & 0.122 & 0.134 & 0.182 \\
Imports $IM_t$ & 0.081 & 0.090 & 0.130 \\
NFA $\hat b^*_t$ & 0.122 & 0.122 & 0.119 \\
Output gap & 0.064 & 0.115 & 0.339 \\
\bottomrule
\end{tabular}}

\vspace{8pt}
{\footnotesize NFA accumulation is almost identical across regimes; the output gap is not --- peg's output gap moves $\sim$5$\times$ more than float's for the same demand shock, since the interest rate cannot help absorb it.}
\end{columns}

\vspace{4pt}
{\footnotesize \textbf{DC insulation, on impact:} float's $\pi^{DC}_t$ is smallest on impact (0.026\%) --- the augmented-network DC index does dampen the immediate FX cost-push. But float's response is also the \emph{most persistent} (barely decaying by quarter 10), while peg's and managed's both overshoot and reverse sign. On-impact insulation is not the whole story.}

\end{frame}

%==============================================================
\begin{frame}{Results: Welfare Cost by Regime --- The Headline Finding}
%==============================================================

\begin{columns}[t]
\column{0.46\textwidth}
\begin{center}
{\tiny \textbf{Total welfare loss ($\times10^4$, Dynare order-1 moments)}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, xbar, width=6.3cm, height=4.3cm, bar width=13pt,
  symbolic y coords={Peg,Managed,Float}, ytick=data,
  xmin=0, xmax=12.5, xlabel={\tiny welfare loss ($\times10^4$)}, nodes near coords,
  nodes near coords style={font=\tiny}]
\addplot[fill=customgreen!45!white, draw=customgreen!70!black] coordinates {(10.48,Float) (4.19,Managed) (8.67,Peg)};
\end{axis}
\end{tikzpicture}
\end{center}
\column{0.52\textwidth}
\begin{center}
{\tiny \textbf{Decomposition: output gap vs.\ sector dispersion}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, ybar stacked, width=7.2cm, height=4.3cm, bar width=22pt,
  symbolic x coords={Float,Managed,Peg}, xtick=data,
  ymin=0, ymax=12.5, ylabel={\tiny welfare loss ($\times10^4$)},
  legend style={font=\tiny, at={(0.5,1.20)}, anchor=north, legend columns=2}]
\addplot[fill=gray!35] coordinates {(Float,0.19) (Managed,0.43) (Peg,2.34)};
\addlegendentry{Output gap}
\addplot[fill=customgreen!25] coordinates {(Float,0.22) (Managed,0.17) (Peg,0.29)};
\addlegendentry{Disp.\ Resource}
\addplot[fill=customgreen!55] coordinates {(Float,1.59) (Managed,1.01) (Peg,1.61)};
\addlegendentry{Disp.\ Manuf.}
\addplot[fill=customgreen!85!black] coordinates {(Float,8.48) (Managed,2.59) (Peg,4.43)};
\addlegendentry{Disp.\ Services}
\end{axis}
\end{tikzpicture}
\end{center}
\end{columns}

\vspace{6pt}
{\footnotesize \textbf{Welfare measure} (Rubbo Prop.\ 3, adapted): $\mathcal{W}=\tfrac12\big[(\gamma+\varphi)\mathrm{Var}(\tilde y_t)+\sum_i\lambda_{D,i}\varepsilon_i\tfrac{1-\hat\delta_i}{\hat\delta_i}\mathrm{Var}(\pi_{it})\big]$, evaluated on Dynare's own order-1 theoretical variances (see caveat on order vs.\ welfare, two slides back). \textbf{Float has the lowest output-gap cost of all three (0.19) but by far the largest Services-dispersion cost (8.48, driven by the persistence channel above) --- managed float is the only regime that is not dominated on some margin.}}

\end{frame}

%==============================================================
\begin{frame}{Why Floating Costs More Than Expected: Persistence, Not Volatility}
%==============================================================

{\footnotesize \textbf{Mechanism:} under float, $S_t$ is pinned down by UIP and the (highly persistent, autocorrelation 0.994) net-foreign-asset process $\hat b^*_t$. Since $S_t$ enters \emph{every} sector's marginal cost via $\Omega^F_i$, letting the currency float doesn't just insulate against FX shocks --- it also lets \emph{domestic} TFP shocks propagate through a new, slow-decaying exchange-rate channel that does not exist under a peg ($S_t\equiv0$).}

\begin{center}
{\tiny \textbf{$\pi^{DC}_t$ response to a Services (sector 3) TFP shock}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, width=10.5cm, height=4.1cm,
  xlabel={\tiny Quarters}, ylabel={\tiny $\pi^{DC}_t$ (\%)},
  xmin=0.5, xmax=10.5, xtick={1,...,10},
  legend style={font=\tiny, at={(0.97,0.03)}, anchor=south east, row sep=-3pt}]
\addplot[thick, gray!40, dotted] coordinates {(1,-0.1990)(2,-0.1004)(3,-0.0422)(4,-0.0081)(5,0.0113)(6,0.0218)(7,0.0269)(8,0.0286)(9,0.0284)(10,0.0271)};
\addlegendentry{Peg}
\addplot[thick, gray!60!black, dashed] coordinates {(1,-0.1251)(2,-0.0899)(3,-0.0624)(4,-0.0409)(5,-0.0242)(6,-0.0114)(7,-0.0017)(8,0.0056)(9,0.0108)(10,0.0146)};
\addlegendentry{Managed}
\addplot[thick, customgreen!85!black] coordinates {(1,-0.1333)(2,-0.1173)(3,-0.1042)(4,-0.0932)(5,-0.0836)(6,-0.0751)(7,-0.0677)(8,-0.0610)(9,-0.0550)(10,-0.0496)};
\addlegendentry{Float}
\end{axis}
\end{tikzpicture}
\end{center}

{\footnotesize \textbf{Reading:} peg resolves the shock via a fast, one-time adjustment and overshoots/reverses within 3--4 quarters; float's response barely decays over the whole horizon. This is a \emph{pure domestic TFP shock} --- no FX shock to insulate against --- yet float still has the most drawn-out response, since the exchange rate is now a slow state variable feeding continuously back into costs.}

\end{frame}

%==============================================================
\begin{frame}{Which Sector Prefers Which Regime? Two Equations}
%==============================================================

{\footnotesize Two calibratable objects, not one, determine a sector's regime preference --- and in this economy they point in \emph{opposite} directions across sectors.}

\begin{columns}[T]
\column{0.5\textwidth}
{\footnotesize \textbf{1. Direct FX exposure} (network- and rigidity-weighted import share):}
\[
\Gamma_i = \frac{[\Delta(I-\Omega\Delta)^{-1}\bm\omega_F]_i}{\kappa}
\]
{\footnotesize \textbf{2. Welfare weight} (centrality $\times$ stickiness):}
\[
\kappa_i = \lambda_{D,i}\,\varepsilon\,\frac{1-\hat\delta_i}{\hat\delta_i}
\]

\column{0.5\textwidth}
{\tiny
\begin{tabular}{lccc}
\toprule
 & Resource & Manuf. & Services \\
\midrule
$\Gamma_i$ (FX exposure) & \textbf{0.234} & 0.054 & 0.006 \\
$\kappa_i$ (welfare weight) & 0.43 & 5.54 & \textbf{74.6} \\
\bottomrule
\end{tabular}
}
\end{columns}

\vspace{4pt}
{\scriptsize \textbf{The sector most exposed to the exchange rate on impact is the one welfare cares about least; the sector welfare cares about most is almost insulated from it directly.} A peg switches off $\Gamma_i\Delta e_t$ for everyone --- but it does not eliminate adjustment, it \emph{relocates} it to domestic prices, landing on the upstream sector because it sits at the border ($P^H$ is dominated by its price).}

\vspace{3pt}
{\scriptsize \textbf{Net effect (real $\kappa_i\mathrm{Var}^R(\pi_i)$, $\times10^4$):} Resource's relocated-adjustment cost under peg outweighs its avoided $\Gamma$-cost ($0.44\to0.59$) --- so despite the largest $\Gamma_i$, it still prefers \emph{float}. Services is insulated from both channels, so peg nearly halves its inflation variance ($16.96\to8.86$) --- and since $\kappa_3\gg\kappa_1,\kappa_2$, this one sector's preference dominates the aggregate ranking.}

\end{frame}

%==============================================================
\begin{frame}{Sector-Level Winners and Losers}
%==============================================================

\begin{columns}[t]
\column{0.55\textwidth}
\begin{center}
{\tiny \textbf{Each sector's own price-dispersion cost, by regime ($\times10^4$)}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, ybar, width=7.8cm, height=5.0cm, bar width=8pt,
  symbolic x coords={Resource,Manuf.,Services}, xtick=data,
  ymin=0, ymax=9.5, ylabel={\tiny welfare cost (own sector, $\times10^4$)},
  legend style={font=\tiny, at={(0.5,1.14)}, anchor=north, legend columns=3}]
\addplot[fill=customgreen!85!black] coordinates {(Resource,0.219) (Manuf.,1.589) (Services,8.481)};
\addlegendentry{Float}
\addplot[fill=gray!55] coordinates {(Resource,0.166) (Manuf.,1.008) (Services,2.587)};
\addlegendentry{Managed}
\addplot[fill=gray!25] coordinates {(Resource,0.293) (Manuf.,1.608) (Services,4.428)};
\addlegendentry{Peg}
\end{axis}
\end{tikzpicture}
\end{center}
\column{0.40\textwidth}
{\footnotesize \textbf{All three sectors agree on their first choice: managed float.} They disagree on the runner-up:}
\begin{itemize}\setlength{\itemsep}{4pt}
\item \footnotesize \textbf{Resource} (flexible, peripheral, most import-exposed): Managed $>$ Float $>$ Peg. Direct FX exposure makes the peg its worst option.
\item \footnotesize \textbf{Manufacturing}: Managed $\gg$ \{Float $\approx$ Peg\} --- roughly indifferent between the two corner regimes.
\item \footnotesize \textbf{Services} (sticky, central, low import exposure): Managed $>$ Peg $>$ Float. The persistence channel (previous slide) hurts it more than direct FX exposure does, so it would rather fix the exchange rate than float it.
\end{itemize}
\end{columns}

\vspace{4pt}
{\footnotesize \textbf{Key point:} the sector that is most exposed to FX shocks directly (Resource) and the sector with the most at stake in the regime choice overall (Services) are not the same sector, and they even rank the two corner regimes in \emph{opposite} order --- a policymaker averaging across sectors could easily miss this.}

\end{frame}

%==============================================================
\begin{frame}{Sensitivity: The Optimal Degree of FX Stabilization}
%==============================================================

{\footnotesize \textbf{Real sweep, not illustrative:} re-solved the managed-float regime in Dynare for $\phi_s\in[0,2]$ ($\phi_s=0$ is the pure float limit). $\phi_s$ does not affect the steady state, so this isolates the policy trade-off cleanly.}

\vspace{4pt}
\begin{columns}[t]
\column{0.58\textwidth}
\begin{center}
{\tiny \textbf{Total welfare loss vs.\ $\phi_s$ ($\times10^4$)}}\\[2pt]
\begin{tikzpicture}
\begin{axis}[slide fig, width=8.2cm, height=5.0cm,
  xlabel={\tiny FX-stabilization weight $\phi_s$}, ylabel={\tiny welfare loss ($\times10^4$)},
  xmin=-0.05, xmax=2.05, ymin=3.5, ymax=11.0]
\addplot[thick, customgreen!85!black, mark=*, mark size=1.3pt] coordinates {(0.00,10.476)(0.10,4.603)(0.20,4.185)(0.30,4.189)(0.50,4.436)(0.75,4.797)(1.00,5.124)(1.50,5.649)(2.00,6.042)};
\node[font=\tiny] at (axis cs:0.20,3.75) {min at $\phi_s\approx0.20$};
\draw[dashed, gray!50, thin] (axis cs:0.30,3.5) -- (axis cs:0.30,4.189);
\node[font=\tiny, gray!60] at (axis cs:0.55,3.85) {calibrated $\phi_s=0.30$};
\end{axis}
\end{tikzpicture}
\end{center}
\column{0.38\textwidth}
{\footnotesize \textbf{Reading:}}
\begin{itemize}\setlength{\itemsep}{4pt}
\item \footnotesize Going from pure float ($\phi_s=0$) to just $\phi_s=0.10$ more than halves the welfare loss (10.48 $\to$ 4.60).
\item \footnotesize The minimum is flat and wide: $\phi_s\in[0.2,0.3]$ is statistically indistinguishable, and the calibrated value (0.30) is very close to optimal.
\item \footnotesize Beyond $\phi_s\approx0.3$, cost rises again --- too much FX stabilization crowds out output-gap stabilization from the same single interest-rate instrument.
\end{itemize}
\end{columns}

\vspace{4pt}
{\footnotesize \textbf{Bottom line:} a little FX stabilization goes a long way; a lot is counterproductive. Neither corner regime (float or peg) is optimal --- a modest, positive $\phi_s$ is.}

\end{frame}

%==============================================================
\begin{frame}{Summary: Key Messages}
%==============================================================

{\footnotesize
\begin{enumerate}\setlength{\itemsep}{5pt}
\item \footnotesize \textbf{Free float is not the optimal regime, even though it directly targets the DC index.} Managed float has less than half the total welfare loss of pure float (4.19 vs.\ 10.48, $\times10^4$) and beats the hard peg too (8.67). This is the model's own solution, not an assumption.
\item \footnotesize \textbf{Why:} floating turns the exchange rate into a slow, persistent state variable (via UIP and the near-unit-root NFA process) that feeds continuously back into every sector's marginal cost through $\Omega^F_i$. This transforms even purely \emph{domestic} TFP shocks into long, drawn-out inflation, whereas a peg resolves the same shock via a fast one-time price adjustment. \textbf{Persistence, not on-impact volatility, is what drives the welfare cost.}
\item \footnotesize \textbf{Every sector prefers managed float first}, but ranks the two corner regimes oppositely: Resource (import-exposed, flexible, peripheral) ranks float over peg; Services (import-light, sticky, central) ranks peg over float. The sector most exposed to FX shocks and the sector with the most at stake in the regime choice are different sectors.
\item \footnotesize \textbf{The optimal amount of FX stabilization is small but strictly positive}: welfare is minimized around $\phi_s\approx0.2$--$0.3$, with more than half the gain captured by just $\phi_s=0.10$; too much FX stabilization crowds out output-gap stabilization from the same instrument.
\item \footnotesize These are first-order (order-1) welfare comparisons (order-2 pruning fails here due to the price-level/ER unit root implied by an inflation-only Taylor rule) --- rankings should be read as indicative of the mechanism, not certainty-equivalent-exact.
\end{enumerate}}

\end{frame}

%==============================================================
\begin{frame}{Remaining Work}
%==============================================================

{\footnotesize \textbf{Done:}}
{\footnotesize
\begin{tabular}{@{}ll@{}}
$\checkmark$ & Full nonlinear model coded in Dynare; solved (Dynare 7.0, MATLAB) for all three regimes \\
$\checkmark$ & Steady state solved semi-analytically (\texttt{fzero} on a scalar reduced system), not guessed \\
$\checkmark$ & Network objects (Domar weights, import centrality, DC weights) derived, verified against theory \\
$\checkmark$ & Real IRFs, moments, welfare decomposition for float / peg / managed (\texttt{results/*.csv}) \\
$\checkmark$ & Real $\phi_s$ sweep (9 re-solved points); welfare-minimizing $\phi_s\approx0.2$--$0.3$ identified \\
\end{tabular}}

\vspace{8pt}
{\footnotesize \textbf{Remaining (target: July 22):}}
{\footnotesize
\begin{tabular}{@{}ll@{}}
$\square$ & Sensitivity to calibration (alternative $\Omega^F$, $\delta_i$): is managed-float dominance robust? \\
$\square$ & Price-level-anchored rule to get a fully second-order-accurate welfare ranking \\
$\square$ & Formalize the ``ER persistence'' mechanism analytically \\
$\square$ & Write up Sections 4--6 (quantitative results, discussion) \\
\end{tabular}}

\end{frame}

\end{document}
